---
title: "Author preprocessing summary"
author: "`r author`"
date: "`r Sys.Date()`"
output: markdown_document
---

## Authors

 * `r length(unique(df$author))` [unique authors](output.tables/author_accepted.csv) These final names capture all name variants from the custom [author synonyme table](https://github.com/rOpenGov/bibliographica/blob/master/inst/extdata/ambiguous-authors.csv), and exclude known pseudonymes (see below). If multiple names for the same author are still observed on this list, they should be added on the [author synonyme table](https://github.com/rOpenGov/bibliographica/blob/master/inst/extdata/ambiguous-authors.csv).
 * `r sum(!is.na(df$author))` documents have unambiguous author information (`r round(100*mean(!is.na(df$author_name)))`%). 
 * `r length(unique(subset(df.preprocessed, author_pseudonyme)$author))` [unique pseudonymes](output.tables/pseudonyme_accepted.csv) are recognized based on [custom pseudonyme lists](https://github.com/rOpenGov/bibliographica/blob/master/inst/extdata/names/pseudonymes/custom_pseudonymes.csv).
 * [Discarded author names](output.tables/author_discarded.csv) This list should not include any real authors (if it does, please send a note). The following stopword lists are considered when discarding names:
  * [Stopwords for names](https://github.com/rOpenGov/bibliographica/blob/master/inst/extdata/stopwords_for_names.csv)
  * [Stopwords for titles](https://github.com/rOpenGov/bibliographica/blob/master/inst/extdata/stopwords_titles.csv)

[Author name conversions](output.tables/author_conversion_nontrivial.csv) Non-trivial conversions from the original to final names


Top-`r ntop` uniquely identified authors and their productivity (title count).

```{r summaryauthors, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10, out.width='430px', fig.show='hold'}
p <- NULL
p <- top_plot(df, "author", ntop) +
     		  ggtitle(paste("Top authors")) +
		  ylab("Documents")
print(p)

dff = df %>%
      filter(is.na(author) & !is.na(author_name)) %>%
      select(author_name)
p <- top_plot(dff,  "author_name", ntop) + ggtitle("Top discarded authors")
print(p)
```

### Ambiguous authors

Authors with ambiguous living year information - can we spot here
cases where these are clearly known identical or distinct authors?
Should also add living year information from supporting sources later.

[Authors with missing life years](output.tables/authors_missing_lifeyears.csv) (Life year info can be augmented [here](https://github.com/rOpenGov/bibliographica/blob/master/inst/extdata/author_info.csv))

[Authors with ambiguous life years](output.tables/author_life_ambiguous.csv) Some of these might be synonymous and could be added to [author synonyme list](https://github.com/rOpenGov/bibliographica/blob/master/inst/extdata/ambiguous-authors.csv) (the first term will be selected for the final data)


### Life span of uniquely identified top authors

Ordered by productivity (number of documents))

```{r, summaryauthorslife, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
a <- rev(rev(sort(table(df$author)))[1:ntop])
dfa <- df[, c("author", "author_birth", "author_death")]
dfa <- filter(dfa, !is.na(author) & (author %in% names(a)))
dfa <- dfa[!duplicated(dfa), ]
dfa <- dfa[match(names(a), dfa$author),]
dfa <- arrange(dfa, author_birth)
# Order authors by birth year
dfa$author <- factor(dfa$author, levels = dfa$author)
dfa$index <- 1:nrow(dfa)

p <- ggplot(dfa)
p <- p + geom_segment(aes(y = author, yend = author, x = author_birth, xend = author_death), size = 2) 
p <- p + theme(axis.text.y = element_text(size = 9))
p <- p + xlab("Author life span (year)") + ylab("")
print(p)
```


### Author productivity

Title count versus paper consumption (all authors):

```{r authortitlespapers, fig.height=8, fig.width=16, echo=FALSE, warning=FALSE}
res1 <- compare_title_paper(df, "author", plot.mode = "text")
res2 <- compare_title_paper(df, "author", plot.mode = "point")
grid.arrange(res2$plot, res1$plot, nrow = 1)
#kable(res1$table)
```


```{r summaryTop10authorstimeline, fig.height=10, fig.width=20, echo=FALSE}
theme_set(theme_bw(20))
top.authors <- names(top(df, field = "author", n = 3))
dfs <- df %>% filter(author %in% top.authors) %>%
     	 group_by(author, publication_decade) %>%
     	 tally() %>%
     	 arrange(publication_decade)
p <- ggplot(dfs, aes(x = publication_decade, y = n, fill = author)) +
       geom_bar(stat = "identity", position = "stack", color = "black") +
       xlab("Publication Decade") +
       ylab("Title Count") +
       scale_fill_grey() +
       guides(fill = guide_legend("Author")) +
       ggtitle("Title count timeline for the top authors")
print(p)
```




