---
title: "Gender preprocessing overview"
author: "`r author`"
date: "`r Sys.Date()`"
output: markdown_document
---

### Gender

 * [Author-gender mappings](output.tables/author_accepted.csv) in the final data

 * `r length(unique(subset(df.preprocessed, author_gender == "male")$author))` unique male authors
 
 * `r length(unique(subset(df.preprocessed, author_gender == "female")$author))` unique female authors
 
 * `r nrow(subset(df.preprocessed, author_gender == "male"))` documents (`r round(100*nrow(subset(df.preprocessed, author_gender == "male"))/nrow(df.preprocessed), 1)`%) with a male author
 
 * `r nrow(subset(df.preprocessed, author_gender == "female"))` documents (`r round(100*nrow(subset(df.preprocessed, author_gender == "female"))/nrow(df.preprocessed), 1)`%) with a female author
 
 * `r nrow(subset(df.preprocessed, author_gender == "ambiguous" | is.na(author_gender)))` documents (`r round(100*nrow(subset(df.preprocessed, author_gender == "ambiguous" | is.na(author_gender)))/nrow(df.preprocessed), 1)`%) with [unresolved gender](output.tables/author_gender_discarded.csv) (including pseudonymes)

 * [First names identified as female](output.tables/gender_female.csv) in the preprocessed data (including pseudonymes)

 * [First names identified as male](output.tables/gender_male.csv) in the preprocessed data (including pseudonymes)

 * [First names with ambiguous
   gender](output.tables/gender_ambiguous.csv) (both male and female
   listed in the gender mapping tables) in the preprocessed data
   (including pseudonymes). To override and resolve amiguous mappings,
   gender info can be added to the [custom name-gender
   mappings](https://github.com/COMHIS/bibliographica/blob/master/inst/extdata/names/firstnames/custom_gender.csv)
   or the [custom author information
   table](https://github.com/COMHIS/bibliographica/blob/master/inst/extdata/author_info.csv)

 * [First names with unknown gender](output.tables/gender_unknown.csv)
   (no gender mapping info available) in the preprocessed data
   (including pseudonymes). The missing info can be added to the
   [custom name-gender
   mappings](https://github.com/COMHIS/bibliographica/blob/master/inst/extdata/names/firstnames/custom_gender.csv)
   or the [custom author information
   table](https://github.com/COMHIS/bibliographica/blob/master/inst/extdata/author_info.csv)

```{r summary-authorgenders, fig.height=7, fig.width=8, echo=FALSE, warning=FALSE, fig.show='hold', out.width='400px'}
gen <- df %>% select(author, author_gender)
dfs <- gen %>% group_by(author, author_gender) # %>% summarize(n = n())
dfs$author_gender <- as.character(dfs$author_gender)
dfs$author_gender[is.na(dfs$author_gender)] <- "unknown"
for (id in unique(dfs$author_gender)) {
  p <- top_plot(filter(dfs, author_gender == id), "author", ntop) + ggtitle(paste("Top", id, "authors"))
  print(p)
}
```


Author gender distribution in the complete data:

```{r summarygender0, echo=FALSE, message=FALSE, warning=FALSE}
dfs <- df %>% group_by(author_gender) %>%
              summarize(docs = n(), fraction = round(100*n()/nrow(df), 2))
names(dfs) <- c("Gender", "Documents (n)", "Fraction (%)")	      
kable(dfs, digit = 2)
```

Author gender distribution over time. Note that the name-gender mappings change over time and geography but this has not been taken into account here.


```{r summarygendertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
tab <- table(df$author_gender)
dfd <- df %>% group_by(publication_decade) %>% summarize(n.male = sum(author_gender == "male", na.rm = T), n.female = sum(author_gender == "female", na.rm = T), n.total = n()) %>% mutate(p.male = 100*n.male/n.total, p.female = 100*n.female/n.total) %>% filter(n.total > 25 & publication_decade > 1470) 
dfy <- df %>% group_by(publication_year) %>% summarize(n.male = sum(author_gender == "male", na.rm = T), n.female = sum(author_gender == "female", na.rm = T), n.total = n()) %>% mutate(p.male = 100*n.male/n.total, p.female = 100*n.female/n.total) %>% filter(n.total > 25)
library(microbiome)
theme_set(theme_bw(25))
p <- NULL # Avoid confusion if the plot gives error
p <- microbiome::plot_regression(p.female ~ publication_decade, dfd)
p <- p + 
       labs(x = "Publication decade", y = "Female authors (%)") +
       guides(fill = "none", size = "none", color = "none", alpha = "none")
print(p)
```



### Data sources

The [name-gender mappings](https://github.com/COMHIS/bibliographica/blob/master/inst/extdata/gendermap.csv) were collected from the following sources using [this script](https://github.com/COMHIS/bibliographica/blob/master/inst/extdata/data.gender.R):

  * U.S. Social Security Administration baby name data as implemented in the babynames and gender R packages. For each year from 1880 to 2013, the number of children of each sex given each name. All names with more than 5 uses are given.  
  * The U.S. Census data in the Integrated Public Use Microdata Series as implemented in the genderdata R package  
  * The Kantrowitz corpus of male and female names as implemented in the genderdata R package 
  * The genderdata R package mappings for Canada, UK, Germany, Iceland, Norway, and Sweden. 
 * [Multilingual database](http://www.lexique.org/public/prenoms.php) (Prenoms.txt) 
 * [French first names](http://www.excel-downloads.com/forum/86934-liste-des-prenoms.htmlhttp://http://www.excel-downloads.com/forum/86934-liste-des-prenoms.html)
 * [German first names](http://www.albertmartin.de/vornamen/)
 * [Finnish population register](https://www.avoindata.fi/data/fi/dataset/none) (Vaestorekisterikeskus; VRK). First names for living Finnish citizens that live in Finland and abroad in 2016. Only names with frequency n>10 are included. Source: avoindata.fi service and Vaestorekisterikeskus (VRK). Version: 3/2016. Data license CC-BY 4.0.
 * [Pseudonymes](https://github.com/COMHIS/bibliographica/blob/master/inst/extdata/names/pseudonymes/custom_pseudonymes.csv) provided by the authors of the bibliographica R package.
 * [Custom name-gender mappings](https://github.com/COMHIS/bibliographica/blob/master/inst/extdata/names/firstnames/custom_gender.csv) constructed manually by the authors of this R package
 * [Custom author information](https://github.com/COMHIS/bibliographica/blob/master/inst/extdata/author_info.csv) constructed manually by the authors of this R package 


The name-gender mappings from different years and regions are
combined. When the sources give conflicting gender mappings, the
gender is marked to be ambiguous.  Afterwards, our [custom name-gender
mappings](https://github.com/COMHIS/bibliographica/blob/master/inst/extdata/names/firstnames/custom_gender.csv)
and [custom author
information](https://github.com/COMHIS/bibliographica/blob/master/inst/extdata/author_info.csv)
tables are used to augment this information. The genderizeR R package
could also be useful but the genderizer.io API has a limit of 1000
queries a day, hence omitted for now.



