---
title: "Language summaries"
author: "Leo Lahti"
date: "`r Sys.Date()`"
output: markdown_document
---

## Language

 * `r unique(unlist(strsplit(df$language, ";"), use.names=FALSE))-1` [unique languages](output.tables/language_accepted.csv)
 * The languages may come in [combinations](output.tables/language_conversions.csv)
 * `r sum(df$multilingual, na.rm = TRUE)` multilingual documents (`r round(100 * mean(df$multilingual, na.omit = TRUE), 2)`%)  
 * `r sum(is.na(df$languages))` docs (`r round(100*mean(is.na(df$languages)),2)`%) with empty or [unrecognized language](output.tables/language_discarded.csv)

Language codes are from [MARC](http://www.loc.gov/marc/languages/language_code.html); new custom abbreviations can be added in [this table](https://github.com/COMHIS/bibliographica/blob/master/inst/extdata/language_abbreviations.csv).

Title count per language (including multi-language documents):

```{r summarylang, echo=FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=10}
# TODO
```


### Top languages

Number of documents assigned with each language. For a complete list,
see [accepted languages](output.tables/language_accepted.csv).

```{r summarylang2, echo=FALSE, results='asis'}
# TODO
#tab <- top(dfs, "key", output = "data.frame", round = 1)
#colnames(tab) <- c("Language", "Documents (n)", "Fraction (%)")
#kable(head(tab))
```

