---
title: "Preprocessing overview"
author: "`r author`"
date: "`r Sys.Date()`"
output: markdown_document
---

# Preprocessing summary

## Specific fields

  * [Author info](author.md)
  * [Gender info](gender.md)
  * [Publisher info](publisher.md)
  * [Publication geography](publicationplace.md)
  * [Publication year info](publicationyear.md)
  * [Titles](title.md)  
  * [Document sizes](size.md)
  * [Document and subject topics](topic.md)
  * [Languages](language.md)

## Field conversions

This documents the conversions from raw data to the final preprocessed version (accepted, discarded, conversions). Only some of the key tables are explicitly linked below. The complete list of all summary tables is [here](output.tables/).

## Annotated documents

Fraction of documents with data:

```{r summaryannotations, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=8, fig.height=11}
availability <- field_availability(df)
print(availability$plot)
```

Same in exact numbers: documents with available/missing entries, and number of unique entries for each field. Sorted by missing data:

```{r sumtab, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
tab <- availability$table %<>% arrange(n)
names(tab) <- gsub("missing", "missing (%)", names(tab))
names(tab) <- gsub("available", "available (%)", names(tab))
names(tab) <- gsub("^n$", "available (n)", names(tab))
names(tab) <- gsub("unique_entries", "unique (n)", names(tab))
names(tab) <- gsub("field_name", "field name", names(tab))
kable(tab[, c(1, 3, 2, 4, 5)], digits = 1, caption = "Data availability")
```



## Histograms of all entries for numeric variables

```{r summary-histograms, echo=FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=4, fig.show='hold', out.width="200px"}
num <- c(); for (field in names(df)) {num[[field]] <- is.numeric(df[[field]])}
numeric.fields <- setdiff(names(which(num)), c("row.index", "original_row", "unity"))
for (field in numeric.fields) {
  df$fieldtoplot <- df[[field]]
  p <- ggplot(df, aes(x = fieldtoplot))
  p <- p + geom_histogram()
  #p <- p + scale_x_log10()
  p <- p + ggtitle(paste(field, "histogram"))
  p <- p + ylab("Documents")
  #p <- p + xlab(paste(field, "(log10)"))
  p <- p + xlab(field)  
  print(p)
}
```


## Histograms of the top entries for factor variables

Non-trivial factors with at least 2 levels are shown.

```{r summary-bars, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=5, fig.show='hold', out.width="430px"}
fac <- c(); for (field in names(df)) {fac[[field]] <- is.factor(df[[field]])}
factor.fields <- names(which(fac))
for (field in factor.fields) {
  #df$fieldtoplot <- df[[field]]
  n <- min(length(unique(df[[field]])), ntop)
  #p <- top_plot(df, "fieldtoplot", n)
  if (length(n) > 1) {
    p <- top_plot(df, field, n)  
    p <- p + ggtitle(paste("Top ", field))
    p <- p + scale_y_log10()
    p <- p + ylab("Documents (Log10)")
    print(p)
  }
}
```



