---
title: "Preprocessing overview"
author: "`r author`"
date: "`r Sys.Date()`"
output: markdown_document
---

# Summary

Date:

```{r date, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
date()
```


## Specific fields

  * [Author info](author.md)
  * [Gender info](gender.md)
  * [Publisher info](publisher.md)
  * [Publication geography](publicationplace.md)
  * [Generic document info](documents.md)
  * [Document sizes](size.md)
  * [Document topics](topic.md)


## Field conversions

This documents the conversions from raw data to the final preprocessed version (accepted, discarded, conversions). Only some of the key tables are explicitly linked below. The complete list of all summary tables is [here](output.tables/).

## Annotated documents

Fraction of documents with data:

```{r summaryannotations, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=8, fig.height=11}
availability <- field_availability(df)
print(availability$plot)
```

Same in exact numbers: documents with available/missing entries, and number of unique entries for each field. Sorted by missing data:

```{r sumtab, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
tab <- availability$table %<>% arrange(n)
names(tab) <- gsub("missing", "missing (%)", names(tab))
names(tab) <- gsub("available", "available (%)", names(tab))
names(tab) <- gsub("^n$", "available (n)", names(tab))
names(tab) <- gsub("unique_entries", "unique (n)", names(tab))
names(tab) <- gsub("field_name", "field name", names(tab))
kable(tab[, c(1, 3, 2, 4, 5)], digits = 1, caption = "Data availability")
```


Fields of special interest. Real success percentage (proportion of successful conversions compared to non-NA entries in the original data):

```{r missing2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
dfs <- df %>% select(author, publication_place, country, publication_year, publication_year_from, publication_year_till, corporate, area, pagecount, gatherings, width, height, paper.consumption.km2, publisher, self_published)
success <- as.data.frame(t(apply(dfs, 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
original.nonNA <- as.data.frame(t(apply(select(df.orig, publication_place, publication_time, corporate, physical_extent, physical_dimension, publisher, author_name), 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))

# Compare the number of non-NA entries in preprocessed data to number
# of non-NA entries in the original data:
real.success <- c()
real.success[["publication_place"]] <- success$publication_place/original.nonNA$publication_place
real.success[["country"]] <- success$country/original.nonNA$publication_place
real.success[["publication_year"]] <- success$publication_year/original.nonNA$publication_time
real.success[["publication_year_from"]] <- success$publication_year_from/original.nonNA$publication_time
real.success[["publication_year_till"]] <- success$publication_year_till/original.nonNA$publication_time
real.success[["corporate"]] <- success$corporate/original.nonNA$corporate
real.success[["publisher"]] <- success$publisher/original.nonNA$publisher
real.success[["self_published"]] <- success$self_published/original.nonNA$publisher
real.success[["pagecount"]] <- success$pagecount/original.nonNA$physical_extent
real.success[["area"]] <- success$area/original.nonNA$physical_dimension
real.success[["gatherings"]] <- success$gatherings/original.nonNA$physical_dimension
real.success[["author"]] <- success$author/original.nonNA$author
real.success[["paper"]] <- success$paper.consumption.km2/sum(rowMeans(!is.na(df.orig[, c("physical_extent", "physical_dimension")])) == 1)
par(mar = c(3, 8, 2, 1)); barplot(100*sort(real.success), horiz = T, main = "Real success rate (selected fields)", las = 1, xlim = c(0, 100), xlab = "Success rate (%)")
```


## Histograms of all entries for numeric variables

```{r summary-histograms, echo=FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=4, fig.show='hold', out.width="200px"}
num <- c(); for (field in names(df)) {num[[field]] <- is.numeric(df[[field]])}
numeric.fields <- setdiff(names(which(num)), c("row.index", "original_row", "unity"))
for (field in numeric.fields) {
  df$fieldtoplot <- df[[field]]
  p <- ggplot(df, aes(x = fieldtoplot))
  p <- p + geom_histogram()
  #p <- p + scale_x_log10()
  p <- p + ggtitle(paste(field, "histogram"))
  p <- p + ylab("Documents")
  #p <- p + xlab(paste(field, "(log10)"))
  p <- p + xlab(field)  
  print(p)
}
```

## Histograms of the top entries for factor variables

```{r summary-bars, echo=FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=4, fig.show='hold', out.width="200px"}
fac <- c(); for (field in names(df)) {fac[[field]] <- is.factor(df[[field]])}
factor.fields <- names(which(fac))
for (field in factor.fields) {
  #df$fieldtoplot <- df[[field]]
  n <- min(length(unique(df[[field]])), ntop)
  #p <- top_plot(df, "fieldtoplot", n)
  p <- top_plot(df, field, n)  
  p <- p + ggtitle(paste("Top ", field))
  p <- p + scale_y_log10()
  p <- p + ylab("Documents (Log10)")
  print(p)
}
```



