---
title: "Pagecount preprocessing summary"
author: "`r author`"
date: "`r Sys.Date()`"
output: markdown_document
---

```{r init, echo=FALSE}
#opts_chunk$set(comment=NA, fig.width=6, fig.height=6)
opts_chunk$set(fig.path = "figure/size-")
```


## Page counts

  * Page count missing and estimated for `r sum(!is.na(df$pagecount)) - sum(!is.na(df$pagecount.orig))` documents (`r round(100*(sum(!is.na(df$pagecount)) - sum(!is.na(df$pagecount.orig)))/nrow(df), 1)`%).

  * Page count missing and could not be estimated for `r sum(is.na(df.preprocessed$pagecount.orig) & is.na(df.preprocessed$pagecount))` documents (`r round(100 * sum(is.na(df.preprocessed$pagecount.orig) & is.na(df.preprocessed$pagecount))/nrow(df.preprocessed), 1)`%).

  * Page count updated for `r sum(!df$pagecount.orig == df$pagecount, na.rm = T)` documents.
  
  * [Conversions from raw data to final page count estimates](output.tables/pagecount_conversion_nontrivial.csv)

<!--[Page conversions from raw data to final page count estimates with volume info](output.tables/page_conversion_table_full.csv)-->

  * [Discarded pagecount info](output.tables/pagecount_discarded.csv) For these cases the missing/discarded page count was estimated based on average page count estimates for [single volume](mean_pagecounts_singlevol.csv), [multi-volume](mean_pagecounts_multivol.csv) and [issues](mean_pagecounts_issue.csv), calculated from those documents where original pagecount info is available.

  * [Automated tests for page count conversions](https://github.com/rOpenGov/bibliographica/blob/master/inst/extdata/tests_polish_physical_extent.csv)


Left: Gatherings vs. overall pagecounts (original + estimated). Right: Only the estimated page counts (shown only for the `r sum(!is.na(df$pagecount)) - sum(!is.na(df$pagecount.orig))` documents that have missing pagecount info in the original data):

```{r size-estimated, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6, fig.show="hold", out.width="430px"}
theme_set(theme_bw(20))
dfs <- select(df, pagecount, gatherings) 
dfs$pagecount <- as.numeric(gsub(" pages", "", dfs$pagecount))
dfs <- dfs %>% filter(!is.na(pagecount) & !is.na(gatherings))
dfg <- group_by(dfs, pagecount, gatherings) %>% tally()
names(dfg) <- c("pages", "gatherings", "documents")
dfg$gatherings <- factor(dfg$gatherings, levels = levels(df$gatherings))
ylims <- range(dfg$pages)
p <- ggplot(dfg, aes(x = gatherings, y = pages)) 
#p <- p + scale_y_continuous(trans = "log10")
n <- nchar(max(na.omit(table(dfg$pages))))
ylim <- ylim(ylims)
p <- p + scale_y_log10(breaks=10^(0:n))
p <- p + geom_point(aes(size = documents))
p <- p + scale_size(trans="log10")
p <- p + ggtitle(paste("Estimated and original pages\n(n=", sum(dfg$documents), ")", sep = ""))
p <- p + xlab("Size (gatherings)")
p <- p + ylab("Pages (original and estimated)")
p <- p + coord_flip()
print(p)

p <- ggplot(subset(df.preprocessed, is.na(pagecount.orig) & !is.na(pagecount)),
       aes(x = gatherings, y = pagecount)) +
       geom_count() +
       coord_flip() +
       ggtitle(paste("Estimated page counts\n(n=", sum(is.na(df.preprocessed$pagecount.orig) & !is.na(df.preprocessed$pagecount)), ")", sep = "")) +
       xlab("Gatherings") +
       ylab("Estimated page count")
print(p)
```


<!--

## Average page counts (only works in CERL now)

Multi-volume documents average page counts are given per volume.

```{r size-pagecountsmulti, echo=FALSE, message=FALSE, warning=FALSE}
source(system.file("extdata/mean_pagecounts.R", package = "bibliographica"))
kable(mean.pagecounts, caption = "Average page counts", digits = 2)
```

```{r size-pagecountsmulti2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=6}
p <- ggplot(melt(mean.pagecounts[, c("median.pages.multivol", "median.pages.singlevol", "median.pages.issue", "doc.dimension")]), aes(fill = variable, y = value, x = doc.dimension)) 
p <- p + geom_bar(stat = "identity", position = "dodge")
p <- p + ylab("Pages")
p <- p + xlab("")
p <- p + coord_flip()
p <- p + ggtitle("Median page counts")
p1 <- p

p <- ggplot(melt(mean.pagecounts[, c("mean.pages.multivol", "mean.pages.singlevol", "mean.pages.issue", "doc.dimension")]), aes(fill = variable, y = value, x = doc.dimension)) 
p <- p + geom_bar(stat = "identity", position = "dodge")
p <- p + ylab("Pages")
p <- p + xlab("")
p <- p + coord_flip()
p <- p + ggtitle("Mean page counts")
p2 <- p
grid.arrange(p1, p2, nrow = 1)
```

-->
