---
title: "Publisher preprocessing summary"
author: "`r author`"
date: "`r Sys.Date()`"
output: markdown_document
---


### Publishers

 * `r length(unique(df$publisher))` [unique publishers](output.tables/publisher_accepted.csv)

 * `r sum(!is.na(df$publisher))` documents have unambiguous publisher information (`r round(100*mean(!is.na(df$publisher)), 1)`%). This includes documents identified as self-published; the author name is used as the publisher in those cases (if known).

 * `r length(which(df$self_published))` documents are identified as self-published (`r round(100*(length(which(df$self_published))/nrow(df)), 1)`%). 

 * [Discarded publisher entries](output.tables/publisher_discarded.csv)

 * [Conversions from original to final names](output.tables/publisher_conversion_nontrivial.csv) (only non-trivial conversions shown)


The `r ntop` most common publishers are shown with the number of documents. 

```{r summarypublisher2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=9}
p <- top_plot(df, "publisher", ntop)
p <- p + ggtitle(paste("Top publishers"))
p <- p + scale_y_log10()
p <- p + ylab("Documents")
print(p)
```

### Publication timeline for top publishers

Title count

```{r top_pub_timeline, fig.height=10, fig.width=20, echo=FALSE}
# For some reason the ggplot never completes if top n > 2 ???
theme_set(theme_bw(20))
field <- "publisher"
tops <- names(top(df, field, n = 2))
dfs <- df %>% select(field, publication_decade) 
dfs$field <- as.character(dfs[[field]]); dfs[[field]] <- NULL
dfs <- dfs %>% filter(field %in% tops) %>%
               filter(!is.na(field) & !is.na(publication_decade)) %>%
	       count(field, publication_decade)
dfs$field <- as.factor(dfs$field)
p <- ggplot(dfs, aes(x = publication_decade, y = n, fill = field)) +
       geom_bar(stat = "identity", position = "stack", color = "black") +       
       labs(x = "Publication Decade", y = "Title Count",
            title = "Title count timeline for the top publishers") +
       scale_fill_grey() +
       guides(fill = guide_legend("Publisher")) 
# print(p)
```



Title count versus paper consumption (top publishers):

```{r publishertitlespapers, fig.height=8, fig.width=8, echo=FALSE, warning=FALSE}
#res <- compare_title_paper(df, "publisher", selected = tops)
tops <- names(top(df, field = "publisher", n = 10))
res <- compare_title_paper(df, "publisher")
print(res$plot)  
kable(subset(res$table, publisher %in% tops), digit = 2)
```


### Corporates

Summaries of the corporate field.

 * `r length(unique(df$corporate))` [unique corporates](output.tables/corporate_accepted.csv)

 * `r sum(!is.na(df$corporate))` documents have unambiguous corporate information (`r round(100*mean(!is.na(df$corporate)), 1)`%). 

 * [Discarded corporate entries](output.tables/corporate_discarded.csv)

 * [Conversions from original to final names](output.tables/corporate_conversion_nontrivial.csv) (only non-trivial conversions shown)


The `r ntop` most common corporates are shown with the number of documents. 

```{r summarycorporate2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=9}
p <- top_plot(df, "corporate", ntop)
p <- p + ggtitle(paste("Top corporates"))
p <- p + scale_y_log10()
p <- p + ylab("Documents")
print(p)
```



