---
title: "Publisher preprocessing summary"
author: "`r author`"
date: "`r Sys.Date()`"
output: markdown_document
---


### Publishers

[Publishers accepted](output.tables/publisher_accepted.csv)

[Publishers discarded](output.tables/publisher_discarded.csv)

```{r summarypublisher, echo=FALSE, message=FALSE, warning=FALSE}
tab <- top(df, "publisher", output = "data.frame")
```

The `r ntop` most common publishers are shown with the number of documents. Publisher information is available for `r sum(!is.na(df$publisher))` documents (`r round(100*mean(!is.na(df$publisher)))`%). There are `r nrow(tab)` unique publisher names (some may be synonymes, though).


```{r summarypublisher2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=9}
p <- top_plot(df, "publisher", ntop)
p <- p + ggtitle(paste("Top publishers"))
p <- p + scale_y_log10()
p <- p + ylab("Documents")
print(p)
```

### Publication timeline for top publishers

Title count

```{r summaryTop10pubtimeline, fig.height=10, fig.width=20, echo=FALSE}
theme_set(theme_bw(20))
tops <- names(top(df, field = "publisher", n = 5))
field <- "publisher"
dfs <- df
dfs$field <- dfs[[field]]
dfs <- dfs %>% filter(field %in% tops) %>%
     	 group_by(field, publication_decade) %>%
     	 tally() %>%
     	 arrange(publication_decade)
p <- ggplot(dfs, aes(x = publication_decade, y = n, fill = field)) +
       geom_bar(stat = "identity", position = "stack", color = "black") +
       xlab("Publication Decade") +
       ylab("Title Count") +
       scale_fill_grey() +
       guides(fill = guide_legend("field")) +
       ggtitle("Title count timeline for the top publishers")
print(p)
```

Paper consumption

```{r summaryTop10publisherstimelinepaper, fig.height=30, fig.width=10, echo=FALSE, warning=FALSE}
# Calculate paper consumption for publishers
df2 <- df %>%
    group_by(publisher) %>%
    summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
# Pick top-10 paper publishers
o <- order(df2$paper.consumption.km2, decreasing = TRUE)
top10 <- na.omit(df2$publisher[o])[1:10]
dfs <- filter(df, publisher %in% top10)
dfs <- group_by(dfs, publisher, publication_year) %>%
    summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
p <- ggplot(dfs, aes(x = publication_year, y = paper.consumption.km2)) 
p <- p + geom_bar(stat = "identity") 
p <- p + facet_grid(publisher ~ .)
p <- p + ggtitle("Annual paper consumption by top publishers")
print(p)
```



Title count versus paper consumption (top publishers):

```{r publishertitlespapers, fig.height=5, fig.width=10, echo=FALSE, warning=FALSE}
res <- compare_title_paper(df, "publisher", selected = tops)
print(res$plot)  
kable(res$table)
```
