---
title: "Publication place preprocessing summary"
author: "`r author`"
date: "`r Sys.Date()`"
output: markdown_document
---

### Publication places

 * `r length(unique(str_trim(unlist(strsplit(as.character(df$publication_place), ";")))))` [publication places](output.tables/publication_place_accepted.csv)
 * `r length(unique(df$country))` [publication countries](output.tables/country_accepted.csv) 
 * Publication place is identified for `r sum(!is.na(df$publication_place))` documents (`r round(100*mean(!is.na(df$publication_place)))`%). 
 * Publication country is identified for `r sum(!is.na(df$country))` documents (`r round(100*mean(!is.na(df$country)))`%).
 * `r round(100*mean(!is.na(df$latitude) & !is.na(df$longitude)), 1)`% of the documents could be matched to geographic coordinates (based on the [Geonames](http://download.geonames.org/export/dump/) database). See the [list of places missing geocoordinate information](output.tables/absentgeocoordinates.csv). Altogether ```r round(100 * mean(is.na(df.preprocessed$latitude) | is.na(df.preprocessed$longitude)), 2)```% of the documents have missing geocoordinates.
 * [Places with unknown publication country](output.tables/publication_place_missingcountry.csv) (can be added to [country mappings](https://github.com/rOpenGov/bibliographica/blob/master/inst/extdata/reg2country.csv))
 * [Ambiguous publication places](output.tables/publication_place_ambiguous.csv)
 * [Potentially ambiguous region-country mappings](output.tables/publication_country_ambiguous.csv) (these may occur in the data in various synonymes and the country is not always clear when multiple countries have a similar place name; the default country is listed first)
 * [Conversions from the original to the accepted place names](output.tables/publication_place_conversion_nontrivial.csv)
 * [Unknown place names](output.tables/publication_place_todo.csv) These terms do not map to any known place on the [synonyme list](https://github.com/rOpenGov/bibliographica/blob/master/inst/extdata/PublicationPlaceSynonymes.csv); either because they require further cleaning or have not yet been encountered in the analyses
 * [Discarded place names](output.tables/publication_place_discarded.csv) These terms are potential place names but with a closer check explicitly rejected on the [synonyme list](https://github.com/rOpenGov/bibliographica/blob/master/inst/extdata/PublicationPlaceSynonymes.csv)

Top-`r ntop` publication places are shown together with the number of documents.

```{r summaryplace, echo=FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=4, fig.show='hold', out.width='430px'}
p <- top_plot(df, "publication_place", ntop)
p <- p + ggtitle(paste("Top publication places"))
p <- p + scale_y_log10()
p <- p + ylab("Title count")
print(p)

p <- top_plot(df, "country", ntop)
p <- p + ggtitle(paste("Top publication countries"))
p <- p + scale_y_log10()
p <- p + ylab("Title count")
print(p)
```


### Top publication countries	

```{r summaryplace3, echo=FALSE, results='asis'}
tab <- top(df, "country", output = "data.frame", round = 1)
colnames(tab) <- c("Country", "Documents (n)", "Fraction (%)")
kable(head(tab))
```

