---
title: "bibliographica vignette"
author: "Leo Lahti, Niko Ilomaki, Mikko Tolonen"
date: "`r Sys.Date()`"
bibliography: 
- bibliography.bib
- references.bib
output: html_document
---
<!--
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{bibliographica vignette}
  %\usepackage[utf8]{inputenc}
-->


R tools for bibliographic data analysis
===========

Your [contributions](http://ropengov.github.com/contribute.html), [bug
reports and other feedback](https://github.com/ropengov/bibliographica) are
welcome!

## Installation

We assume you have installed [R](http://www.r-project.org/). If you
use [RStudio](http://www.rstudio.com/ide/download/desktop), change the
default encoding to UTF-8. 

Installing the stable release version in R:

```{r install, eval=FALSE}
library(devtools)
install_github("ropengov/bibliographica")
```

Load tools and set UTF-8 encoding

```{r test, message=FALSE, warning=FALSE, eval=TRUE, message=FALSE}
library(bibliographica)
Sys.setlocale(locale="UTF-8") 
```

## Harmonizing textual annotation fields in library catalogues

The preprocessing functions aim to extract information from textual library catalogue annotation fields by approximating the [Bibliographic Processing Cataloging Rules](https://www.libraries.psu.edu/psul/cataloging/training/bpcr/300.html). 


### Dimension information

```{r dimensions, message=FALSE, eval=TRUE}
# Pick the dimension fields:
res <- polish_dimensions("1/2to (37 x 11 cm)")
library(knitr)
knitr::kable(res)

# Also estimate and fill in the missing fields where possible:
res <- polish_dimensions("1/2to (37 x 11 cm)", fill = TRUE)
knitr::kable(res)
```


### Page information

```{r pages, message=FALSE, warning=FALSE, eval=TRUE}
polish_pages("[6],viii,386p. ;")$estimated.pages
```

### Volume information

Pick information on volume numbers and counts:

```{r voln, message=FALSE, warning=FALSE, eval=TRUE}
polish_volumenumber("v.4")
```

```{r volc, message=FALSE, warning=FALSE, eval=TRUE}
polish_volumecount("4v.")
```


### Stopwords

Removing stopwords (for a full list of stopword functions, see [here](https://github.com/rOpenGov/bibliographica/blob/master/R/stopwords.R)):

```{r stopw, message=FALSE, warning=FALSE, eval=TRUE}
remove_stopwords(c("a", "well", "james", "30 year war"), terms = "well", remove.letters = TRUE)
```

### Dimension table

Document dimensions (gatherings, width, height) can be estimated when this information is only partially available. The estimation is made based on ready-made mapping tables. The table can be changed by the user but by default the functions use this mapping:

```{r dimtab, message=FALSE, warning=FALSE, eval=TRUE}
kable(dimension_table())
```

### Sheet size table

Estimate sheet area in cm2:

```{r sheetarea2}
sheet_area("folio")
```

Sheet sizes are calculated according to the sheet dimension table. The table can be changed by the user (see the function arguments) but by default the functions use this mapping:

```{r sheetarea, message=FALSE, warning=FALSE, eval=TRUE}
kable(sheet_area())
```

## Licensing and Citations

This work can be freely used, modified and distributed under the 
[Two-clause BSD license](http://en.wikipedia.org/wiki/BSD\_licenses).

```{r citation, message=FALSE}
citation("bibliographica")
```

## Session info

This vignette was created with

```{r sessioninfo, message=FALSE, warning=FALSE}
sessionInfo()
```
