---
title: "BIBLIOGRAPHICA vignette"
author: "Leo Lahti, Niko Ilomaki, Mikko Tolonen"
date: "`r Sys.Date()`"
bibliography: 
- bibliography.bib
- references.bib
output: html_document
---
<!--
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{bibliographica Vignette}
  %\usepackage[utf8]{inputenc}
-->

R tools for bibliographic data analysis
===========

Your [contributions](http://ropengov.github.com/contact.html) and [bug
reports and other feedback](https://github.com/ropengov/bibliographica) are
welcome!

## Installation

We assume you have installed [R](http://www.r-project.org/). If you
use [RStudio](http://www.rstudio.com/ide/download/desktop), change the
default encoding to UTF-8. 

Install the stable release version in R:

```{r install, eval=FALSE}
library(devtools)
install_github("ropengov/template")
```

Load tools

```{r test, message=FALSE, warning=FALSE, eval=TRUE}
library(template)
```

Set UTF-8 encoding

```{r locale, eval=FALSE}
Sys.setlocale(locale="UTF-8") 
```


### Harmonizing manual fields data

The preprocessing functions approximate the [Bibliographic Processing Cataloging Rules](https://www.libraries.psu.edu/psul/cataloging/training/bpcr/300.html).

Polish dimension information:

```{r dimensions, message=FALSE, eval=TRUE}
#polish_dimensions("1/2⁰ (37 x 11 cm)")
```

Polish page information:

```{r pages, message=FALSE, warning=FALSE, eval=TRUE}
polish_pages("[6],viii,386p. ;")$estimated.pages
```

## Licensing and Citations

This work can be freely used, modified and distributed under the 
[Two-clause BSD license](http://en.wikipedia.org/wiki/BSD\_licenses).

```{r citation, message=FALSE, eval=TRUE}
citation("bibliographica")
```

## Session info

This vignette was created with

```{r sessioninfo, message=FALSE, warning=FALSE}
sessionInfo()
```
